Word Sense Disambiguation\\ \small{Leveraging the NLTK Toolkit and External Tools}

### 2011-04-14 paper/paper.tex
fixed conflicts
Baseline graph discussion added. w00t

Dependency parsing is fairly slow, requiring about a second per instance to run
on a computer running an Atom D525 processor (which is fairly underpowered, but
modern).  To help alleviate this problem, we wrote a system that saves parses
for each context, and only calls the parser if it observes a new parse, so we
could reuse parsing information across runs of our program.  Because this file
is several hundred megabytes in size, it is not included in our submitted code.
\subsection{Collocation}

@@

>>>>

Dependency parsing is fairly slow, requiring about a second per instance to run
on a computer running an Atom D525 processor (which is fairly underpowered, but
modern).  To help alleviate this problem, we wrote a system that saves parses
for each context, and only calls the parser if it observes a new parse, so we
could reuse parsing information across runs of our program.  Because this file
is several hundred megabytes in size, it is not included in our
submitted code.

\subsection{Collocation}

@@

Figure \ref{fig:base} shows our results for running just the Decision
Tree classifier and the \naive{} Bayes classifier with no features
enabled. With no bootstrapping, the Decision Tree classifier has a
much higher f-measure. With bootstrapping, the Decision Tree
classifier decreases in f-measure while the \naive{} Bayes classifier
improves in f-measure.
